Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-04-29 paper.tex
Added references bibtex file

\documentclass[]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
% \usepackage{txfonts}

\begin{document}
\title{Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing}
\author{}
\date{\today}
\maketitle

@@

\section{Introduction}

\subsection{General spherical density profile $\rho(r)$}
Using thin lens approximation

Projected surface density at radius R
\[\Sigma(R) = \int_{-\infty}^{\infty}{\rho(\sqrt{R^2 + z^2}) dz}\]

@@

Ellipticity
\[\epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}\]

@@

\[\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_C}{(r/r_s)\left(1 + r/r_s\right)^2}\]

\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
[Bartelmann 2001]

\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2} \left(
    \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
\right)\]

@@

\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]

\[\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2} \left(
    \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) + \ln{\left(\frac{\theta/\theta_s}{2}\right)}
\right)\]

@@

We switch the dependence to $M_{200}$ and $C$ with:

\[\delta_C = \frac{200}{3} \frac{C^3}{\ln(1 + C) - C/(1 + C)}\]
\[r_s = \frac{r_{200}}{C}\]
\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
\[C = \frac{r_{200}}{r_s}\]

@@

>>>>

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{graphicx}
% \usepackage{txfonts}

\graphicspath{ {figures/} }

\begin{document}

\title{Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing}
\author{Ian Holst and Doyee Byun}
\date{\today}
\maketitle

@@

\section{Introduction}
Background/history of this research topic, goals for this section

\subsection{General spherical density profile $\rho(r)$}
Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.

Projected surface density at radius R
\[\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}\]

@@

Ellipticity
\[\epsilon_i = \frac{2 \gamma_i/(1 - \kappa)}{1 + \gamma^2/(1 - \kappa)^2}\]
\[\epsilon =  -\epsilon_1 \cos{2\phi} -\epsilon_2 \sin{2\phi}\]

@@

\[\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}\]

\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
[Bartelmann 2001]

\[\overline{\Sigma}_\mathrm{NFW}(R) = \frac{4 \rho_\mathrm{crit} \delta_c r_s}{(R/r_s)^2} \left(
    \frac{2}{\sqrt{(R/r_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) + \ln{\left(\frac{R/r_s}{2}\right)}
\right)\]

@@

\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]

\[\overline{\Sigma}_\mathrm{NFW}(\theta) = \frac{4 \rho_\mathrm{crit} \delta_c D_L \theta_s}{(\theta/\theta_s)^2} \left(
    \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} ~\arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) + \ln{\left(\frac{\theta/\theta_s}{2}\right)}
\right)\]

@@

We switch the dependence to $M_{200}$ and $c$ with:

\[\delta_c = \frac{200}{3} \frac{c^3}{\ln(1 + c) - c/(1 + c)}\]
\[r_s = \frac{r_{200}}{c}\]
\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
\[c = \frac{r_{200}}{r_s}\]

@@

\bibliographystyle{plainnat}
\bibliography{references}
